TBD

### 2016-10-07 paper.tex
nearing the end of redirivation of redundant stefcal

\subsection{Complex GN and LM}
In this section we discuss how we can use the GN and LM algorithms to solve Eq.~\eqref{eq:red_least_squares_complex} (i.e. estimate $\breve{\bz}$). The complex Jacobian is defined to be
\begin{equation}
\label{eq:Jacobian}
\bJ = \begin{bmatrix}
       \bJ & \bJ^*\\
       \conj{\bJ}^* & \conj{\bJ} 
      \end{bmatrix},
\end{equation}
where 
\begin{align}
\bJ &= \frac{\partial \bv}{\partial \bz}, & \bJ^* &= \frac{\partial \bv}{\partial \conj{\bz}}. 
\end{align}
In Eq.~\eqref{eq:Jacobian}, $\frac{\partial}{\partial \bz}$ and $\frac{\partial}{\partial \conj{\bz}}$ respectively denote the cogradient operator and the conjugate cogradient operator (cite Sorber).
The GN update step is now defined as:
\begin{equation}
\label{eq:GN_update}
 \Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\br}.
\end{equation}
The LM update rule is very similar, the major difference being a damping factor $\lambda$ is introduced:
\begin{equation}
\Delta \breve{\bz} = (\bJ^H\bJ + \lambda\bD)^{-1}\bJ^H\breve{\br},
\end{equation}
where $\bD=\bI\odot\bJ^H\bJ$. 
NEED TO MENTION THE SILENT INDEX $k$ AND HOW THE UPDATE RULE IS ITERATIVE. ALSO MENTION THAT $\lambda$ IMPROVES THE CONVERGENCE PROPERTIES. WE WILL REFER TO $\bJ^H\bJ$ AS THE 
HESSIAN.

@@

It is now trivial to compute the Hessian $\bJ^H\bJ$ by using Eq.~\eqref{eq:Jacobian_red}. If we substitute Eq.~\eqref{eq:Jacobian_red} into $\bJ^H\bJ$
we obtain 
\begin{equation}
\bH = \bJ^H\bJ = 
\begin{bmatrix}
\bA & \bB\\
\conj{\bB} & \conj{\bA}
\end{bmatrix},
\end{equation}
where

@@

Furthermore, substituting Eq.~\eqref{eq:Jacobian_red} into $\bJ^H\breve{\br}$ results in
\begin{equation}
\bJ^H\breve{\br} = \begin{bmatrix}
                   \ba & \bb & \conj{\ba} & \conj{\bb}\\
                   \end{bmatrix}^T,
\end{equation}
where
\begin{align}
\left [ \ba \right ]_i &= \sum_{k\neq i} g_k \widetilde{y}_{ik}r_{ik},  & \left [ \bb \right ]_i &= \sum_{pq\in\mathcal{PQ}_i}\conj{g}_p g_q r_{pq},
\end{align}
and
\begin{equation}
\widetilde{y}_{ik} = 
\begin{cases}
\conj{y}_{\zeta_{ik}} & \textrm{if}~k > i\\
y_{\zeta_{ik}} & \textrm{otherwise}
\end{cases}.
\end{equation}

@@

The following identities,
\begin{align}
\label{eq:identities}
\frac{1}{3}\bJ\breve{\bz} &= \breve{\bv}, & \bJ^H\breve{\bv} &= (\bI\odot\bH)\breve{\bz} 
\end{align}
are trivially established by mechanically showing that the left hand side of each identity in Eq.~\eqref{eq:identities} is equal to its right hand side.

The first identity in Eq.~\eqref{eq:identities} can now be used to simplify Eq.~\eqref{eq:GN_update} as follows:
\begin{align}
\Delta \breve{\bz} &= (\bJ^H\bJ)^{-1}\bJ^H(\breve{\bd}-\breve{\bv})\\
&=(\bJ^H\bJ)^{-1}\bJ^H\breve{\bd}-\frac{1}{3}\breve{\bz}
\end{align}

STILL NEED TO ADD z k+1 EXPRESSION.

@@

The natural question now arises: is it possible to derive a redundant calibration variant of the SteFCal algorithm if we follow a similar approach to what \citet{Smirnov2015}
proposed? We now attempt to try and answer that exact question:

>>>>

\subsection{Complex GN and LM}
In this section we discuss how we can use the GN and LM algorithms to solve Eq.~\eqref{eq:red_least_squares_complex} (i.e. estimate $\breve{\bz}$). The complex Jacobian is defined to be
\begin{equation}
\label{eq:Jacobian}
\bJ = \begin{bmatrix}
       \bJ & \bJ^*\\
       \conj{\bJ}^* & \conj{\bJ} 
      \end{bmatrix},
\end{equation}
where 
\begin{align}
\bJ &= \frac{\partial \bv}{\partial \bz}, & \bJ^* &= \frac{\partial \bv}{\partial \conj{\bz}}. 
\end{align}
In Eq.~\eqref{eq:Jacobian}, $\frac{\partial}{\partial \bz}$ and $\frac{\partial}{\partial \conj{\bz}}$ respectively denote the cogradient operator and the conjugate cogradient operator (cite Sorber).
The GN update step is now defined as:
\begin{equation}
\label{eq:GN_update}
 \Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\br}.
\end{equation}
The LM update rule is very similar, the major difference being a damping factor $\lambda$ is introduced:
\begin{equation}
\label{eq:LM_update}
\Delta \breve{\bz} = (\bJ^H\bJ + \lambda\bD)^{-1}\bJ^H\breve{\br},
\end{equation}
where $\bD=\bI\odot\bJ^H\bJ$. 
NEED TO MENTION THE SILENT INDEX $k$ AND HOW THE UPDATE RULE IS ITERATIVE. ALSO MENTION THAT $\lambda$ IMPROVES THE CONVERGENCE PROPERTIES. WE WILL REFER TO $\bJ^H\bJ$ AS THE 
HESSIAN.

@@

It is now trivial to compute the Hessian $\bJ^H\bJ$ by using Eq.~\eqref{eq:Jacobian_red}. If we substitute Eq.~\eqref{eq:Jacobian_red} into $\bJ^H\bJ$
we obtain 
\begin{equation}
\label{eq:red_H}
\bH = \bJ^H\bJ = 
\begin{bmatrix}
\bA & \bB\\
\conj{\bB} & \conj{\bA}
\end{bmatrix},
\end{equation}
where

@@

Furthermore, substituting Eq.~\eqref{eq:Jacobian_red} into $\bJ^H\breve{\br}$ results in
\begin{equation}
\bJ^H\breve{\br} = \begin{bmatrix}
                   \ba & \bb & \conj{\ba} & \conj{\bb}\\
                   \end{bmatrix}^T,
\end{equation}
where
\begin{align}
\label{eq:ab}
\left [ \ba \right ]_i &= \sum_{k\neq i} g_k \widetilde{y}_{ik}r_{ik},  & \left [ \bb \right ]_i &= \sum_{pq\in\mathcal{PQ}_i}\conj{g}_p g_q r_{pq},
\end{align}
and
\begin{equation}
\widetilde{y}_{ik} = 
\begin{cases}
\conj{y}_{\zeta_{ik}} & \textrm{if}~k > i\\
y_{\zeta_{ik}} & \textrm{otherwise}
\end{cases}.
\end{equation}

@@

The following identities,
\begin{align}
\label{eq:identities}
\frac{1}{3}\bJ\breve{\bz} &= \breve{\bv}, & \bJ^H\breve{\bv} &= \widetilde{\bH}\breve{\bz} 
\end{align}
are trivially established by mechanically showing that the left hand side of each identity in Eq.~\eqref{eq:identities} is equal to its right hand side.
In Eq.~\eqref{eq:identities}, $\widetilde{\bH}$ denotes $\bI\odot\bH$.

Replacing $\breve{\br}$ with $\breve{\bd}-\breve{\bv}$ in Eq.~\eqref{eq:GN_update} results in
\begin{equation}
\label{eq:temp_GN_eq}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H(\breve{\bd}-\breve{\bv}), 
\end{equation}
Substituting the first identity of Eq.~\eqref{eq:identities} into Eq.~\eqref{eq:temp_GN_eq} and simplifying we obtain
\begin{equation}
\label{eq:two_thrids}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd}-\frac{1}{3}\breve{\bz}.
\end{equation}
It now trivially follows from Eq.~\eqref{eq:two_thrids} that:
\begin{equation}
\breve{\bz}_{k+1} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd} + \frac{2}{3}\breve{\bz}_{k}. 
\end{equation}
%STILL NEED TO ADD z k+1 EXPRESSION.
THE TAKE HOME HERE IS WE CAN CALCULATE THE UPDATE STEP WITHOUT CALCULATING THE RESIDUAL.

@@

The natural question now arises: is it possible to derive a redundant calibration variant of the SteFCal algorithm if we follow a similar approach to what \citet{Smirnov2015}
proposed?

Inspecting Eq.~\eqref{eq:red_H} reveals that in the case of redundant calibration the Hessian's diagonal entries are also more significant than its off-diagonal entries.
If we substitute $\bJ^H\bJ$ with $\widetilde{\bH}$ (by its diagonal approximation) and replace $\breve{\br}$ with $\breve{\bd} - \breve{\bv}$ in Eq.~\eqref{eq:GN_update} we obtain
\begin{equation}
\label{eq:appr_GN}
 \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H(\breve{\bd}-\breve{\bv})
\end{equation}
Utilizing the second identity in Eq.~\eqref{eq:identities} allows us to simplify Eq.~\eqref{eq:appr_GN} to
\begin{equation}
  \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}-\breve{\bz}.
\end{equation}
It now trivially follows that
\begin{equation}
 \breve{\bz}_{k+1} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}.
\end{equation}
We obtain a similar result if we repeat the above procedure, only in this case we use Eq.~\eqref{eq:LM_update} instead,
namely
\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k, \label{eq:alpha}  
\end{align}
where $\alpha = \frac{1}{1+\lambda}$. Moreover, $\lambda = \frac{1-\alpha}{\alpha}$. The analytic expression of $\bJ^H\breve{\bd}$ will be very similar to the analytic 
expression of $\bJ^H\breve{\br}$, the only difference being that in Eq.~\eqref{eq:ab} the letter $r$ would be replaced by a $d$. If we substitute the analytic expression
of $\bJ^H\breve{\bd}$ and $\widetilde{\bH}^{-1}$ (which is easily computed as the matrix is a diagonal matrix) into Eq.~\eqref{eq:alpha} we obtain the following two update rules:
\begin{equation}
\label{eq:g_update}
g_{i}^{k+1} = \alpha \frac{\sum_{j\neq i} g_j^k \widetilde{y}_{ij}^{~\!\!k} d_{ij}}{\sum_{j\neq i} |g_j^k|^2|y_{\zeta_{ij}}^k|^2} + (1-\alpha) g_i^k, 
\end{equation}
and
\begin{equation}
\label{eq:y_update}
y_{i}^{k+1} = \alpha \frac{\sum_{pq \in \mathcal{PQ}_i} \conj{g}_p^k g_q^k d_{pq}}{\sum_{pq \in \mathcal{PQ}_i}|g_p^k|^2|g_q^k|^2} + (1-\alpha) y_i^k 
\end{equation}

Interestingly enough, if we substitute $\alpha = 1$ into Eq.~\ref{eq:g_update} then it reduces to the skymodel-based StEFCal update rule .

\begin{eqnarray}
\begin{bmatrix} \Delta \boldsymbol{z}\\ \Delta \conj{\boldsymbol{z}} \end{bmatrix} &\approx& \widetilde{\boldsymbol{H}}^{-1}\boldsymbol{J}^H(\breve{\boldsymbol{d}}-\breve{\boldsymbol{v}})\\ 
&=& \widetilde{\boldsymbol{H}}^{-1}\boldsymbol{J}^H\breve{\boldsymbol{d}} -  \widetilde{\boldsymbol{H}}^{-1}\widetilde{\boldsymbol{H}}\breve{\boldsymbol{z}}\\
\breve{\boldsymbol{z}}_{k+1} &\approx& \widetilde{\boldsymbol{H}}^{-1}\boldsymbol{J}^H\breve{\boldsymbol{d}}
\end{eqnarray}

Levenberg-Marquardt:

\begin{eqnarray}
\breve{\boldsymbol{z}}_{k+1} &\approx& \frac{1}{1+\lambda}\widetilde{\boldsymbol{H}}^{-1}\boldsymbol{J}^H\breve{\boldsymbol{d}} + \frac{\lambda}{1+\lambda} \breve{\boldsymbol{z}}_k\\
 &=& \alpha \widetilde{\boldsymbol{H}}^{-1}\boldsymbol{J}^H\breve{\boldsymbol{d}} + (1-\alpha)\breve{\boldsymbol{z}}_k 
\end{eqnarray}

with $\alpha = \frac{1}{1+\lambda}$. Moreover $\lambda = \frac{1-\alpha}{\alpha}$. So in Marthi and Chengular (2014) they use an $\alpha$ of 0.3, which corresponds to an LM damping factor $\lambda$
of $2\frac{1}{3}$.
